\documentclass{article}

\author{Georg, Rudolf (my imaginary fren)}
\date{24.12.2025}
\title{A bedtime story for children}

\begin{document}
\pagenumbering{gobble}
\maketitle
\newpage
\pagenumbering{arabic}

\section{The Dragon and the Wolf}

Once upon a time there was a city located at the rim of the ocean. The coast was rocky and only the most sturdy plants would grow in the cold climate for it was a city in the north where only few people would dare to go as many mythological creatures lived there. 

\subsection{The Awakening of the Dragon}

\paragraph{The dragon cave}Below the cliffs in a cave there slept a dragon. It was one of the ancient type.
\paragraph{The dragon}
Very black and very fierceful. Noone dared to go near it... Except a Wolf who one time in a winter when there was no food went to see him. As he was sleeping the wolf tapped its mighty shoulder which was covered by scales shimmering in all colours even in the dim light of the cave. 

\subsection{The end of the dragon}
The end of the dragon has not yet come. To call it forth on would need several things. 
\paragraph{Courage} To kill a dragon, courage is required. One does not simply kill it one has to mean it as well!
\paragraph{Equipment} One will need sufficient equipment to do so. There are three main categories:
\subparagraph{Weapons} Swords axes and the like. Skyrim teaches us that a sneaky bow might be more than useful.
\subparagraph{Food} To not be hungry when the dragon is upon you is of the most utter importance.
\subparagraph{Something to fight for} If you stand there and the thing you will come home to is Netflix and some Cheetos you will not stand a chance. Think o your family and friends (like me and rudolph) or aquire some of that along the wayy to the cave!
\end{document}
